
### Use your head()

<br>

Welcome!  

In this tutorial you will use the R language to summarise and visualize basic variables. You will be using a data set which contains the variables
`r colnames(mydata)`.  

These variables are saved together in a single data frame object called mydata. Don't worry if the term data frame sounds strange, it is only a kind of table. You can for example see the first three rows of this table like so:
  
```{r}
head(x=mydata, n=3)
```

Here we called the function `head()`, which wants us to give it inside the parenthesis two specific things: `x` and `n`. these are the arguments of the function. Once we told `head()` that `x=mydata` and `n=3`, it knew that we wanted the first three rows of mydata.

In R you can also save any function output by using the assign operator `<-`. Below we define our own new variable mydata_top3 by saving the output of `head()` to it.

```{r}
mydata_top3 <- head(mydata, 3)
```

Notice that when we gave `head()` the information about `x` and `n` in the right order, we didn't have to explicitly state which is which.  

Now that we have our variable saved, we can acces that variable later and for example print it by typing it's name.

```{r}
mydata_top3
```

  
### Exercise 1

<br>

Let's try it! Use `head()` to display the first 10 rows of mydata. Then save this output to a new variable called `ans`.  

Once you have received a green feedback, click Next to proceed to the next part of the tutorial, where you will take a closer look at your variables!

```{r, include=FALSE, echo=FALSE}
# correct answer. echo=FALSE means that this code will not be displayed.
dontlook[[1]] <<- head(mydata,10)
```

